draftFiguresPaper

### 2025-10-20 draftFiguresPaper.Rmd
add dataset
save datasets for Figure2

@@

@@

>>>>

## save this dataset for further analyses
write.csv(datasetClassificationCountries_long_clean, "output/datasetClassificationCountries_long_clean.csv", row.names = F)

@@

# add region from natural earth

library(rnaturalearth)

# .
# .
# .

@@

## save this dataset for further analyses
write.csv(surveyCountries_long_clean, "output/datasetSurveyCountries_long_clean.csv", row.names = F)
